Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-28 docs/manuscript/manuscript.tex

Improving water accessibility has been a priority by many organizations, realizing it is the basic human right to have clean and accessible drinkable water in the past 15 years. From 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fuller2016tracking}. However, some researchers raise concerns on lack of clarity with the global water accessibility monitoring \citep{onda2012global, jia2016highresolution}. However, in an era of rapidly changing technologies, international and government policies, the older researches are not adequate. For an example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest (SDGs) providing clean and accessible drinking water for all by 2030, researchers have devoted their studies to understand water accessibility at global and specific country levels. Several research and studies have focused global water accessibility ,and its progress \citep{sorensonSafeAccessSafe2011,bainAccountingWaterQuality2012,wssccWaterSanitationHygiene2014,  onda2012global, bartram2014global, onda2014country, who2015drinkingwater,fuller2016tracking, weiyuyuGlobalPerspectiveDrinkingwater2016, grahamAnalysisWaterCollection2016,overboOnplotDrinkingWater2016}. While there have been studies focusing on the local community in different parts of the country learning about their water accessibility and sanitation initiation \citep{jagals2006does, geereDomesticWaterCarrying2010, sima2013water, ho2014challenge, sakisakaIntroductionCommunityWater2015, jia2016highresolution}. Where majority raised concerns about the lack of monitoring sustainable water accessibility measurements for many people and some argue for a focus on many people's access to drinking water sources. Nonetheless, there is a lack of robust study on transportation to enhance water accessibility for all people by 2030. 

>>>>

Improving water accessibility has been a priority by many organizations, realizing it is the basic human right to have clean and accessible drinkable water in the past 15 years. From 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fuller2016tracking}. However, some researchers raise concerns on lack of clarity with the global water accessibility monitoring \citep{onda2012global, jia2016highresolution}. However, in an era of rapidly changing technologies, international and government policies, the older researches are not adequate. For an example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest (SDGs) providing clean and accessible drinking water for all by 2030, researchers have devoted their studies to understand water accessibility at global and specific country levels. Several research and studies have focused global water accessibility ,and its progress \citep{sorensonSafeAccessSafe2011,bainAccountingWaterQuality2012,pickering2012freshwater,wssccWaterSanitationHygiene2014,  onda2012global, bartram2014global, onda2014country, who2015drinkingwater,fuller2016tracking, weiyuyuGlobalPerspectiveDrinkingwater2016, grahamAnalysisWaterCollection2016,overboOnplotDrinkingWater2016}. While there have been studies focusing on the local community in different parts of the country learning about their water accessibility and sanitation initiation \citep{jagals2006does, geereDomesticWaterCarrying2010, sima2013water, ho2014challenge, sakisakaIntroductionCommunityWater2015, jia2016highresolution}. Where majority raised concerns about the lack of monitoring sustainable water accessibility measurements for many people and some argue for a focus on many people's access to drinking water sources. Nonetheless, there is a lack of robust study on transportation to enhance water accessibility for all people by 2030. 
